\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-27 pldi/draft.tex
fix

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Parallelizability Classes}.
    Broadly, \unix commands can be broken down into to four classes according to their parallelizability properties.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llll}
\toprule % 28 + 9 + 13 + 105
Class                    &  Key    & Examples                                    & Coreutils              & POSIX       \\
\midrule
Stateless                & ~\tsta  & \tti{tr},   \tti{cat},    \tti{grep}        &  22 (21.1\%)           & 28 (18\%)          \\  % 22
Parallelizable Pure      & ~\tpur  & \tti{sort}, \tti{wc},     \tti{uniq}        &  8 (7.6\%)}            & 9  (5\%)          \\  % 21
Non-parallelizable Pure  & ~\tnpu  & \tti{sha1sum}                               &  13 (12.4\%)}          & 13 (8.3\%)          \\  % 27
Side-effectful           & ~\tsid  & \tti{env},  \tti{cp}, \tti{whoami}          &  57 (58.8\%)           & 105(67.8\%)            \\  % 25
% Irreversible     & ~\tirr  & \tti{exit}, \tti{lpr},    \tti{reboot}      &  5  (0.4\%)     & 5  (0.4\%)           \\  % 5
% \midrule
% Shell PL Constructs             &                         &                  \\
% \etc                            &                         &                  \\
\bottomrule
\end{tabular*}
\label{tab:classes}
\end{table}

>>>>

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Parallelizability Classes}.
    Broadly, \unix commands can be broken down into to four classes according to their parallelizability properties.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llll}
\toprule
Class                    &  Key    & Examples                                    & Coreutils              & POSIX       \\
\midrule
Stateless                & ~\tsta  & \tti{tr},   \tti{cat},    \tti{grep}        &  22 (21.1\%)           & 28 (18\%)        \\  % 22
Parallelizable Pure      & ~\tpur  & \tti{sort}, \tti{wc},     \tti{uniq}        &  8 (7.6\%)            & 9  (5\%)          \\  % 21
Non-parallelizable Pure  & ~\tnpu  & \tti{sha1sum}                               &  13 (12.4\%)          & 13 (8.3\%)       \\  % 27
Side-effectful           & ~\tsid  & \tti{env},  \tti{cp}, \tti{whoami}          &  57 (58.8\%)           & 105(67.8\%)          \\  % 25
% Irreversible     & ~\tirr  & \tti{exit}, \tti{lpr},    \tti{reboot}      &  5  (0.4\%)     & 5  (0.4\%)           \\  % 5
% \midrule
% Shell PL Constructs             &                         &                  \\
% \etc                            &                         &                  \\
\bottomrule
\end{tabular*}
\label{tab:classes}
\end{table}
